\documentclass[letterpaper,10pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{etoolbox}
\usepackage{framed,tabularx,array}
\robustify\cftdotfill

\definecolor{shadecolor}{gray}{0.7} 
\definecolor{shadecolorB}{gray}{0.93}

%-----------------------------------------------------------
%Margin setup

\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}

%-----------------------------------------------------------

\newcommand{\resitem}[1]{
    \item #1 \vspace{-2pt}
}

\newcommand{\resheading}[1]{
    \vspace{8pt}
    \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
        \begin{shaded}
            \setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{
                \textbf{
                    \sffamily{
                        \mbox{~}\makebox[6.5in][l]{\large #1} \vphantom{
                            p\^{E}}
                        }
                    }
                }
            }
        \end{shaded}
  }\vspace{-5pt}
}

\newcommand{\ressubheading}[4]{
    \begin{tabular*}{7in}{
        l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		    \textbf{#1} & #2 \\
		    \textit{#3} & #4 \\
    \end{tabular*}
    \vspace{-6pt}}
    
\newcommand{\ressubheadingtabx}[4]{
    \begin{tabularx}{6.5in}{X<{\cftdotfill{\cftsecdotsep}}@{}r}
        \textbf{#1} & #2 \\
        \textit{#3} & \textit{#4} \\
    \end{tabularx}\vspace{-6pt}}
    
%-----------------------------------------------------------

\begin{document}

%------------------------------------------------------------------------

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Elliott Indiran} & \textbf{Computational Linguist} \\
github, linkedin: eindiran & eindiran@uchicago.edu \\
site: https://eindiran.github.io/ & (805) 651-9333 \\

\end{tabular*}

%------------------------------------------------------------------------

\resheading{Education}

\ressubheading{University of Chicago}{Chicago, Illinois}{Bachelor of the Arts in Linguistics with General Honors}{2011 - 2015}
\begin{itemize}
    \resitem{3.44 Cumulative GPA; 3.67 Fourth-Year GPA}
    \resitem{Relevant coursework: Introduction to Programming for Linguistics, Statistical Methods and Applications, Mathematical Modelling for Linguistics, Computer Science with Applications sequence, and Computational Linguistics.}
    \resitem{Strong linguistics background in syntax, semantics, phonology, phonetics, and morphology.}
\end{itemize}

\ressubheading{Linguistic Society of America}{Chicago, Illinois}{Summer Institute at the University of Chicago}{2015}
\begin{itemize}
	\resitem{Relevant coursework: Exploiting Web Data for Linguistic Research, Unsupervised Learning of Linguistic Structure, Advanced Probabilistic Modeling in R, Speech Technologies, Computational Psycholinguistics, Computational Lexical Semantics.}
\end{itemize}

%------------------------------------------------------------------------

\resheading{Work Experience}

\ressubheading{Computational Linguist at Promptu Systems}{Menlo Park, California}{Promptu Systems Corporation}{October 2015 - present}
\begin{itemize}
    \resitem{Worked on speech recognition projects in English, Italian, German, and Mandarin; both as a software engineer, writing components of the recognizer system, and as a linguist, handling language modeling and writing lexicons and grammars. This included constructing language model training datasets products in several significantly different problem domains.}
    \resitem{Wrote the component of the recognizer system responsible for handling lexicon lookups during entity registration, generating pronunciations wherever possible to avoid needing to perform G2P on out-of-vocab entries. With pre-G2P in place, the number of entities that needed G2P on first registration step dropped drastically, shaving seconds off of the recognizer's start-up latency.}
    \resitem{Led a project to construct a build system for language models, introducing new types of testing and automating work that was previously done by hand. This project used Jenkins to automatically build and test language model training datasets and language models, substantially reducing the frequency of bugs and regressions in the recognizer related to the LM and keeping over a dozen projects up-to-date while not under active development.}
    \resitem{Wrote and maintained a large number of developer tools for use in team; most notably I wrote a fully-featured Java application for recording speech. The recording app needed a lot of special features, so I designed, wrote and tested it entirely from scratch (using the Java Sound API). The app was designed to be useful for recording scripts of phrases, either in a car or in-office.}
    \resitem{Got experience refactoring large, old codebases in C, Perl, Python 2/3 and Java.}
    \resitem{Led a project to speed up the construction on language models. Rewrote the piece of software which was the bottleneck, reducing LM build times by as much as 20x for some datasets. Further decreased the build time of the LMTD by parallelizing the whole process, reducing build times by hours per day.}
    \resitem{Drafted a proposal for changing the build process of a major software component which allowed a substantial number of developer hours to be saved each time a new Acoustic scorer was built, saving upwards of several man-weeks per year.}
\end{itemize}

\ressubheading{Intern with the Linguistic Society of America Summer Institute}{Chicago, Illinois}{Linguistic Society of America (LSA)}{June 2015 - August 2015}
\begin{itemize}
	\resitem{Wrote the software responsible for managing grades and credit assignment at the institute, which was used to process class data for hundreds of participants across nearly 100 classes.} 
	\resitem{Aided the directors of the institute in all technical matters; led tech support during registration.}
	\resitem{Managed a critical registration site for institute participants, ensuring that technical problems did not lead to issues for participants checking in.}
\end{itemize}

\iffalse
\ressubheading{Research Assistant with the Comprehensive Care Program}{Chicago, Illinois}{University of Chicago Hospitals}{May 2014 - January 2015}
\begin{itemize}
	\resitem{Managed large amounts of data using industry-standard software including Excel, Redcap, and Epic; this included handling sensitive data, such as medical records and survey data used for research.}
	\resitem{Conducted hundreds of patient interviews, both over the phone and in clinical settings. The patients were often combative and aggressively did not want to take the required surveys, so this required me to get very good at diffusing customer anger.}
	\resitem{Trained other research assistants how to do patient interaction as well as data management and cleanup.}
\end{itemize}
\fi

\iffalse
\ressubheading{Assistant Director of Strategy for CAM Creative}{Chicago, Illinois}{The Chicago Academy of Music}{June 2013 - January 2014}
\begin{itemize}
	\resitem{Co-founded a project working to build mobile medical clinics which would provide cost-free medical care to neighborhoods with poor access to doctors throughout Chicago.}
	\resitem{Worked closely with small-business owners and community organizers in Woodlawn to foster community outreach programs and in Hyde Park in order to secure a building for the school.}
	\resitem{Wrote grant and funding proposals for the organization, as well as managing project reports and project budgets.}
	\resitem{Designed the logo, menu, and decor at a restaurant and helped launch it. The restaurant is now one of the premier locations in Hyde Park for baked goods.}
\end{itemize}
\fi

\iffalse
\item \ressubheading{Volunteer Internship with The Red Shirt Program}{Oxnard, California}{St. John's Regional Medical Center}{October 2009 - June 2011}
\begin{itemize}
	\resitem{Worked to ensure ongoing patient satisfaction in a variety of clinical environments.}
	\resitem{Became comfortable dealing with extremely high-pressure work environments in the Emergency room.}
\end{itemize}
\fi

%------------------------------------------------------------------------

\resheading{Projects}

\begin{itemize}
    \resitem{With another two software engineers, I founded Sitrus, a quantified-self data collection and analysis tool. We built out the tool with the goal of allowing people who wouldn't normally be willing to put in the investment in QS might try it out if the barrier to entry was incredibly low. Our current task to find all the ways in which the barrier to entry is artificially high and find ways to bring it down.}
    	\resitem{I led Sitrus through Y Combinator's 2018 Startup School class, which we graduated from in November 2018. While in SS 2018, my group of 20 to 30 companies elected me as the moderator for the group; during the course I was responsible for organizing all of the tasks, meetings, homework and discussions for all companies in our section. Due to my diligence in herding everyone to show up and participate, our group had an abnormally high rate of graduation and an abnormally high rate of receiving funding after the program.}
    \resitem{Frequent contributor to a few Open Source projects, including the Coconut Programming Language and related tooling. Have written a substantial amount of documentation for both the Coconut tutorial and main docs.}
    
    \iffalse
    \resitem{Run a small personal website for hosting projects and posts.}
    \fi
    
    \resitem{AutoWater and AudoFeeder: a project to automate watering houseplants and to automate feeding fish respectively. Used a fair amount of electronics knowledge plus Arduino programming.}
    \resitem{orgmode-to-anki: automatically convert notes taken using emacs orgmode, ie from the note taking app Orgzly, into Anki flash cards. Very useful for always automatically moving vocab in your notes onto flashcards.}
    \resitem{Mancala: play mancala in the terminal against another human or against an AI that uses a min-max algorithm to prune possibilities of the game tree.}
\end{itemize}

%------------------------------------------------------------------------

\resheading{Technical Skills}

\begin{itemize}
    \resitem{Have used Java, Python, Perl, and C professionally in production systems. I have built and maintained a large continuous delivery pipeline using Jenkins, scripting with Groovy. Familiar with *nix utilities for system administration tasks, primarily on Linux.}
    \resitem{Python for scripting, data scraping and manipulation, and backend web-development (using Django), with PostgreSQL and MongoDB.}
    \iffalse
    \resitem{Familiar with C++, Javascript, Haskell, Coconut, and Nim.}
    \fi
\end{itemize}

%------------------------------------------------------------------------

\end{document}
